Evaluation of classical correlation functions from 2/3D images on CPU and GPU architectures: introducing CorrelationFunctions.jl

### 2023-09-22 paper-correlations.tex
changes in programm description

{\bf PROGRAM SUMMARY} \\
\begin{small}
\noindent
{\em Program Title:} CorrelationFunctions.jl \\
{\em CPC Library link to program files:} (to be added by Technical Editor) \\
{\em Developer's repository link:}
\url{https://github.com/fatimp/CorrelationFunctions.jl} \\
{\em Code Ocean capsule:} (to be added by Technical Editor)\\
{\em Licensing provisions:} MIT \\
{\em Programming language:} Julia \\
{\em Supplementary material:} \\
{\em Nature of problem:} Correlation functions are invaluable universal
statistical descriptors of structure of porous media used in many scientific
field such as astronomy, soil physics, hydrology and biology. We propose an open
source and cross-platform solution for computation of vast majority of
correlation functions for both 2D and 3D images of porous material. \\
{\em Solution method:} Our package computes correlation functions using fast
Fourier transform using such preprocessing steps as cluster labeling or edge
detection if needed. Almost all of proposed algorithms can be executed on both
CPU and GPU which results in high execution speed on modern hardware. Two
approaches to evaluation of correlation functions are proposed: computation of
correlation maps and computation along predefined directions. These two
approaches can be thought of as an execution time - memory trade-off. \\
\end{small}

>>>>

{\bf PROGRAM SUMMARY} \\
\begin{small}
\noindent
{\em Program Title:} CorrelationFunctions.jl \\
{\em CPC Library link to program files:} (to be added by Technical Editor) \\
{\em Developer's repository link:}
\url{https://github.com/fatimp/CorrelationFunctions.jl} \\
{\em Code Ocean capsule:} (to be added by Technical Editor)\\
{\em Licensing provisions:} MIT \\
{\em Programming language:} Julia \\
{\em Supplementary material:} Numerous Jupiter notebooks with examples are available on the GitHub page\\
{\em Nature of problem:} Correlation functions are invaluable universal
statistical descriptors of structures used in numerous scientific
fields such as astronomy, material science, rock and soil physics, hydrology and biology, to name just a handful of examples. While computational approaches
are available in the literature for some functions, they are fragmented and are usually implemented in proprietary
interpreted languages for CPU architecture alone. \\
{\em Solution method:} We contribute an open
source and cross-platform solution with well documented API for computation of all classical
correlation functions from both 2D and 3D images on CPU and GPU architectures. The package computes correlation functions using two approaches: : computation of
correlation maps and computation along predefined directions. These two
approaches can be thought of as an execution time - memory trade-off, but the choice may also depend on the application.
The computations are based on fast Fourier transform with preprocessing steps as cluster labeling or edge
detection, and linear scan approach to evaluate correlation functions along predefined directions. Where justified, the algorithms can be executed on both
CPU and GPU which results in high execution speed on modern hardware. \\
\end{small}
